\documentclass[12pt]{amsart}

\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=1.1in, tmargin=1in, bmargin=1in]{geometry}

\pagestyle{myheadings}
%\markleft{Syllabus for Math 331, Spring 2020}
%\markright{Syllabus for Math 331, Spring 2020}

\newcommand{\spacer}{\vspace{.2cm}}
\newcommand{\svs}{\vspace{.1cm}}

\newcommand{\red}[1]{\textcolor{red}{#1}}
\definecolor{gold}{rgb}{0.80,0.68,0.00}\newcommand{\gold}[1]{\textcolor{gold}{#1}}

\begin{document}

\thispagestyle{empty}

\noindent\hrulefill
\begin{center}
\Large{\textsc{Math 244 Calculus VI} }\\
\textsc{Study Guide}\\
\small{Created by Pierre-Olivier Paris{\'e}, Inspired by Malik Younsi's study guide}
\end{center}
\hrulefill \\

\section*{Before Each Class}
\textit{Lecture time is limited, so it must be used efficiently. Much of your learning must take place outside of the classroom. You are expected to be prepared as detailed below.}
	\begin{itemize}
	\item Review your notes from the class before, in order to make sure you understand the material that has already been covered.
	\item Read the appropriate section(s) of the textbook \textbf{before} the material is presented in class. This will greatly improve your understanding of the lectures.
	\end{itemize}
	
\section*{After Each Class}
\textit{For each hour in class, you should spend at least two or more hours studying outside the classroom.}
	\begin{itemize}
	\item Carefully reread your lecture notes and the examples therein.
	\item Review the animations placed in the lecture notes and try them by yourself. 
	\item Attempt all of the homework problems and all suggested problems (appearing at the end of each sections in the lecture notes.)
	\item If you don't have time to give a shot at all the suggested problems, then I suggest you to try at least 5 problems in each set.
	\item Try not to look at the solutions before attempting a problem!
	\item Don't hesitate to ask your TA or myself for help during our respective office hours.
	\end{itemize}
	
\section*{Before an exam}
\textit{You won't have a lot of time to complete the problems on the exam (50min). Make sure to arrive prepared, so you don't unexpectedly loose time on a problem. Follow the tips below to prepare yourself.}
	\begin{itemize}
	\item Reread your lecture notes. Make sure you understand all the examples that we did during the lectures. You can try to redo the examples by yourself and compare your solutions to the one given in class. 
	\item Try by yourself the animation made with DESMOS and placed in the lecture notes. This will help you visualize what we did.
	\item Summarize the material of each week. In this way, you will have a great overview of all the material that was covered. You can use a mindmap to create your summary or just a short list.
	\item Retry the homeworks and worksheets problems. The problems on the exam will be really similar to the homeworks and worksheets problems.
	\item Retry the suggested problems of each section. Make sure that you understand the problems that you got wrong. 
	\item Study with a friend, you can quiz each other on the material!
	\end{itemize}

\end{document}